The influence of resource use on yield versus sale price trade-off in Australian vineyards

### 2024-05-20 Cover Letter/main.tex
fixed cover letter for plos one instead of climate

\hfill
\begin{tabular}{l @{}}
	$26^{th}$ January, 2023\\ % Date
	\textbf{Bryce Ronald William Boyd $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\begin{tabular}{@{} l}
	\textbf{Professor Bojie Fu,}\\
	Editor-in-Chief \\
	Geography and Sustainability\\
\end{tabular}

@@

Dear Professor Bojie Fu,
\\~\\
\parskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\centering \textbf{Submission of Manuscript for Consideration by \\Geography and Sustainability}\\
\bigskip % Vertical whitespace
\justifying
\newline \noindent
We wish to submit a new manuscript entitled "\textit{The influence of resource use on yield versus sale price trade-off in Australian vineyards}" for consideration by Geography and Sustainability.
\newline \noindent
In this manuscript we explore natural resource use in agricultural wine production, emphasising sustainability in the trade-off between the sale price and quantity of product. We explore the economic and environmental risks induced by producing grapes at greater yields. We find that lower grape sale price is not solely related to the overall expenditure of resources but rather to efficient management, as well as regional and seasonal variations. We use novel, extensive nationwide data from Australia, collected over a decade by Sustainable Winegrowing Australia. We construct and analyse several models of the multifaceted, multi-resource nature of vineyard management. 
\newline \noindent
We believe that this manuscript is appropriate for publication by Geography and Sustainability as it demonstrates the sustainability of different winegrowing production strategies across winegrowing regions in Australia. These results illustrate the relationship between human interaction and the environment as driven by agricultural management strategies and the resources required to achieve the necessary outcomes to maintain economic sustainability using environmental resources. Thank you for your consideration of this manuscript.
\bigskip \noindent% Vertical whitespace

\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Boyd (corresponding author) on behalf of all coauthors: Kate Helmstedt, Mardi Longbottom, Madeline Mitchell, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}

>>>>

\hfill
\begin{tabular}{l @{}}
	$17^{th}$ May, 2024\\ % Date
	\textbf{Bryce Ronald William Boyd $|$ PhD Candidate}\\
	Queensland University of Technology \\
	School of Mathematical Sciences\\~\\
	Address: Level 8 Y Block, 2 George Street, \\
	Brisbane, Queensland, Australia, 4000\\
	Phone: +61 400 310 105 \\
	Email: bryce.polley@awri.com.au
\end{tabular}

@@

\begin{tabular}{@{} l}
	\textbf{Editorial board,}\\
	PLOS ONE\\
\end{tabular}

@@

Dear members of the editorial board,
\\~\\
\parskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\centering \textbf{Submission of Manuscript for Consideration by \\PLOS ONE}\\
\bigskip % Vertical whitespace
\justifying
\newline \noindent
We wish to submit a new manuscript entitled "\textit{The influence of resource use on yield versus sale price trade-off in Australian vineyards}" for consideration by PLOS ONE.
\newline \noindent
In this manuscript we explore natural resource use in agricultural wine production, emphasising sustainability in the trade-off between the sale price and quantity of product. We explore the economic and environmental risks induced by producing grapes at greater yields. We find that lower grape sale price is not solely related to the overall expenditure of resources but rather to efficient management, as well as regional and climatic variations. We use novel, extensive nationwide data from Australia, collected over a decade by Sustainable Winegrowing Australia. We construct and analyse several models of the multifaceted, multi-resource nature of vineyard management. 
\newline \noindent
We believe that this manuscript is appropriate for publication by PLOS ONE as it demonstrates the sustainability of different winegrowing production strategies across Australian winegrowing regions. These results illustrate the relationship between human interaction and the environment as driven by agricultural management strategies and the resources required to achieve the necessary outcomes to maintain economic sustainability using environmental resources. Thank you for your consideration of this manuscript.
\bigskip \noindent% Vertical whitespace

\includegraphics[scale=0.1]{signature_block.png}
\newline \noindent
Bryce Boyd (corresponding author) on behalf of all coauthors: Kate Helmstedt, Mardi Longbottom, Kerrie Mengersen\\
\newline \noindent
\textit{Corresponding Author}, \textit{Queensland University of Technology}
